---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# varameta

The goal of varameta is to provide estimators for the variance sample median. This enables use of software such as `metafor` for meta-analysis, as current tools in meta-analysis require the effect and the variance of the effect.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

# Thoughts

- Start issues when I connect to the internet. 
- From email from Luke, end of 2017: Howdy Trouble, do you mind running another simulation to get some more coverage plots for the t distribution?  It would be good to look at whats happens as the degrees of freedom changes.  Theory suggests that the mean should be well approximated but the SD not when df is small.  So perhaps look at coverage for df from 1, 2, 5, 10, 20 to see what happens.  Cheers  Cap'n
