---
title: "Replication of Hozo et al.'s Results"
author: "Charles T. Gray"
date: "`r dontpanic::title_date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(varameta)
library(tidyverse)
```

# Tasks

- Find the hozo replication pdfs and include them. 
- Identify all simulation results as presented by Hozo. 
    - 200 random samples
    - sample sizes 8 to 100
    - $~N(\mu = 50, \sigma^2 = 17^2)$
    - $~LN(\mu = 4, \sigma = 0.3)$
    - $~beta(a = 9, b = 4)$
    - $~\exp(\lambda = 10)$
    - $~Weibull(a = 2, b = 35)$
    - plotted average relative error vs sample size
    - mean: formulas (4) and (5)
    - variance: formula (16) and range/4, range/6.
- *What distributions? Build them into the data generation file. (Testing on smaller set, on hold.)*
- ~~Write hozo parameters to data for package?~~


# Take a look at the distributions to simulate over.

```{r See distributions}

rdists %>% {
  tibble(
    distribution = map_chr(., "rdist"),
    par_1 = map_dbl(., c(2, 1)),
    par_2 = map(., c(2, 2))
  )
} %>% knitr::kable()

```

# Simulate data

```{r Set trials}
trials <- 10 # Set low for testing.

```


```{r}
# Hozo pars.
hozo_pars <- cross(list(
  rdists = rdists,
  n = seq(8, 100, by = 2),
  trial = c(1:trials)
))

# Convert to a tibble.
hozo_sim <- hozo_pars %>% {
  tibble( # Using numbers for testing.
    rdist = map_chr(., c("rdists", "rdist")),
    rpars = map(., c("rdists", "rpars")),
    n = map_dbl(., "n"),
    trial = map_int(., "trial")
  )
}

hozo_sim %>% head() %>% knitr::kable()

```

```{r}
# Tally to check we have the correct number of things.
hozo_sim %>% 
  count(rdist, n) %>% 
  filter(nn != trials) %>% 
  nrow() == 0L # Perhaps add this to testing?
```

## Generate samples 

```{r Samples}
hozo_sim <- hozo_sim %>% 
  mutate(ss = pmap(list(n, rdist, rpars), dontpanic::sample_summary),
         summary = map(ss, "summary"),
         sample = map(ss, "sample"))

```

# Calculate estimators

```{r Estimators}

```

